---
title: "Homework 8"
author: "Mahima Mahajan"
date: "2025-04-11"
output:
  pdf_document: default
  html_document: default
---
# **EID :** mkm4582
# **[GitHub repo link (CLICK)](https://github.com/mahimaKmahajan/SDS_315_HW8)**

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
options(warn=-1)

library(boot)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

# **Problem 1.** regression warm up

## Part A
```{r, echo=FALSE, results=FALSE}
creatinine <- read.csv("creatinine.csv")

linReg <- lm(creatclear ~ age, data = creatinine)

summary(linReg)
```
When we use the lm() function calculator in R, a linear regression model, we get the output of 147.81 as the intercept and -0.61 as the rate of creatine clearance in patients depending on age. This gives us the equation *creatclear = -0.62(age) + 147.81*. Using this equation, when a patients age is 55, their expected creatine clearnace rate is about 113.72 mL/min. 

## Part B

When we use the lm() function in R, the summary displaces the rate-- which we used in Part A. The creatine clearance rate is -0.62 mL/min per year, which means that a patient's creatine clearance rate decreases by about 0.62 mL/min every year. 

## Part C

Using the equation from Part A: _creatclear = -0.62(age) + 147.81_

**40 year-old patient calculations:**

creatclear = -0.62(age) + 147.81

135 = -0.62(40) + 147.81

135 > 123.01

Difference = 11.99

**60 year-old patient calculations:**

creatclear = -0.62(age) + 147.81

112 = -0.62(60) + 147.81

112 > 110.61

Difference = 1.39

The 40 year-old is healthier for their age because their creatine clearance is 11.99 higher than expected, compared to the 1.39 difference from the 60 year-old patient.

# **Problem 2.** Modeling disease growth

```{r, echo=FALSE, results=FALSE}
covid <- read.csv("covid.csv")

# Italy exponential growth model
italy <- lm(log(deaths) ~ days_since_first_death, data = covid %>% filter(country == "Italy"))
summary(italy)

# Spain exponential growth model
spain <- lm(log(deaths) ~ days_since_first_death, data = covid %>% filter(country == "Spain"))
summary(spain)
```

## Part 1
For Italy, the estimated growth rate for deaths caused by COVID is 0.183 and the doubling time is 3.8 days. 

## Part 2
For Spain, the estimated growth rate for deaths caused by COVID is 0.276 and the doubling time is 2.5 days. 

## Part 3
```{r, echo=FALSE}
ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) + geom_line() + labs(title = "Reported COVID Deaths over Time", x = "Days Since First Death", y = "Daily Deaths over Time", color = "Country")

```

# **Problem 3.** price elasticity of demand
```{r, echo=FALSE, results=FALSE}
milk <- read.csv("milk.csv")

milk <- milk %>%
  mutate(log_price = log(price),
         log_sales = log(sales))

model <- lm(log_sales ~ log_price, data = milk)
summary(model)

```

The estimated price of elasticity of demand for milk is -1.62. 
